Figures to insert in text

### 2018-04-03 Chapters/Chapter02.tex
Swedish guys 1

The classification algorithm had some problems classifying the letters ``i'' and ``l''. It may have happened because of the low distance between them. In this case, SDM could not differentiate the details --- it has only considered the big picture. Although this behavior is close to how humans see things, we also have the ability to zoom and focus on the details, clearly discerning letter ``i'' from letter ``l''.

@@

% \subsection{Multiple levels}

@@

A hypercube with n dimensions can be divided by two hypercubes with $n-1$ dimensions. Is there an algorithm that separates the area of each hard location in such a form that there exists a function mapping each bitstring in $\{0,1\}^n$ to the set of hard locations it `belongs to'?  Though this would break Kanerva's assumption of a randomly yet uniformly distributed set of hard locations --- for a perfectly symmetrical set of hard locations ---, there could be large performance gains if such a mapping function from a bitstring to its corresponding set of nearest hard locations exists.

>>>>

The classification algorithm had some problems classifying the patterns ``i'' and ``l'', due to the low distance between them. In this case, SDM could not discriminate the differences --- it has only considered the big picture. Although this behavior is close to how humans see things, we also have the ability to zoom and focus on the details, clearly discerning letter ``i'' from letter ``l''.

@@

% \subsection{Deep learning, multiple SDMs, and the animal behavior of Dr. Linhares}

@@

A hypercube with n dimensions can be divided by two hypercubes with $n-1$ dimensions. Is there an algorithm that separates the area of each hard location in such a form that there exists a function mapping each bitstring in $\{0,1\}^n$ to the set of hard locations it `belongs to'?  Though this would break Kanerva's assumption of a randomly yet uniformly distributed set of hard locations --- for a perfectly symmetrical set of hard locations ---, there could be large performance gains if such a mapping function from a bitstring to its corresponding set of nearest hard locations exists. Note that others have attempted heuristic approaches to this\footnote{\citet{Kanerva2009} has recently mentioned that `The computationally most efficient implementation of it, by \citet{Karlsson95afast}, is equivalent to the RAM-based WISARD of  \citet{aleksander1982computer}.' Note, however, that Karlsson's model seems to require $O(2^n)$ hard-locations, and may introduce non-uniform asymmetries in the space.}.
